Probabilistic Forecasting of the Disturbance Storm Time Index: An Autoregressive Gaussian Process approach

### 2017-03-16 agutmpl.tex
Penultimate changes 2

Figures \ref{fig:CompareMae} and \ref{fig:CompareCC} show how the mean absolute error and coefficient of correlation as calculated on the validation set storm events of Table \ref{table:validationstorms}, vary with increasing model order for GP-AR and GP-ARX. The results are represented as boxplots, in which a rectangle is drawn to represent the first and third quartiles, with a vertical line inside to indicate the median value while outlying points are shown as dots. In both cases, the predictive performance first improves and then stagnates or worsens with increasing model order.

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth]{Compare-mae.png}
\caption{Mean Absolute Error on validation set storms vs model order for GP-AR and GP-ARX. \\ \textbf{Key}: Rectangle borders represent the second and third quartiles, with a horizontal line inside to indicate the median value while outlying points are shown as dots}
\label{fig:CompareMae}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth]{Compare-cc.png}
\caption{Coefficient of Correlation on validation set storms vs model order for GP-AR and GP-ARX \\ \textbf{Key}: Rectangle borders represent the second and third quartiles, with a horizontal line inside to indicate the median value while outlying points are shown as dots}
\label{fig:CompareCC}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth]{Compare-mae-arx.png}
\caption{Mean Absolute Error on validation set storms vs model order for GP-AR and GP-ARX for \emph{CSA}, \emph{GS} and \emph{ML} model selection routines \\ Rectangle borders represent the second and third quartiles, with a horizontal line inside to indicate the median value while outlying points are shown as dots}
\label{fig:CompareMaeARX}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth]{Compare-cc-arx.png}
\caption{Coefficient of Correlation on validation set storms vs model order for GP-AR and GP-ARX for \emph{CSA}, \emph{GS} and \emph{ML} model selection routines \\ Rectangle borders represent the second and third quartiles, with a horizontal line inside to indicate the median value while outlying points are shown as dots}
\label{fig:CompareCCARX}
\end{figure}

>>>>

Figures \ref{fig:CompareMae} and \ref{fig:CompareCC} show how the mean absolute error and coefficient of correlation as calculated on the validation set storm events of Table \ref{table:validationstorms}, vary with increasing model order for GP-AR and GP-ARX. The results are represented as box and whisker plots, in which a rectangle is drawn to represent the first and third quartiles, with a horizontal line inside to indicate the median value, outlying points are shown as dots while the whiskers indicate the smallest and largest non-outliers. In both cases, the predictive performance first improves and then stagnates or worsens with increasing model order.

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth]{Compare-mae.png}
\caption{Mean Absolute Error on validation set storms vs model order for GP-AR and GP-ARX. \\ \textbf{Key}: Rectangle borders represent the first and third quartiles, with a horizontal line inside to indicate the median value, outlying points are shown as dots and whiskers indicate the smallest and largest non-outliers}
\label{fig:CompareMae}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth]{Compare-cc.png}
\caption{Coefficient of Correlation on validation set storms vs model order for GP-AR and GP-ARX \\ \textbf{Key}: Rectangle borders represent the first and third quartiles, with a horizontal line inside to indicate the median value, outlying points are shown as dots and whiskers indicate the smallest and largest non-outliers}
\label{fig:CompareCC}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth]{Compare-mae-arx.png}
\caption{Mean Absolute Error on validation set storms vs model order for GP-AR and GP-ARX for \emph{CSA}, \emph{GS} and \emph{ML} model selection routines \\ \textbf{Key}: Rectangle borders represent the first and third quartiles, with a horizontal line inside to indicate the median value, outlying points are shown as dots and whiskers indicate the smallest and largest non-outliers}
\label{fig:CompareMaeARX}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth]{Compare-cc-arx.png}
\caption{Coefficient of Correlation on validation set storms vs model order for GP-AR and GP-ARX for \emph{CSA}, \emph{GS} and \emph{ML} model selection routines \\ \textbf{Key}: Rectangle borders represent the first and third quartiles, with a horizontal line inside to indicate the median value, outlying points are shown as dots and whiskers indicate the smallest and largest non-outliers}
\label{fig:CompareCCARX}
\end{figure}
